### 2017-03-08 MSSM/MSSM.tex
Fixing spacing in itemize env and really sorting the page numbering
Final bits before submission

\chapter{\texorpdfstring{Search for MSSM \AHtotautau}{Search for MSSM A/H -->tautau}}
\label{chap:mssm}
In this chapter the search for neutral Higgs bosons \PHiggs or \PHiggsps
decaying to a pair of tau leptons will be discussed. The results presented
here correspond to those from an analysis peformed on a dataset collected
during the first half of the 2016 p-p running period of the \ac{LHC} \cite{CMS-PAS-HIG-16-037}. %This dataset
%corresponds to an integrated luminosity of $12.9\,\invfb$, and the analysis is
%detailed in reference \cite{CMS-PAS-HIG-16-037}. 
The \etau, \mutau, \tautau and \emu final
states of the di-tau pair were studied. The results of this search are 
model-independent upper limits on \xsbr of \PHiggs or \PHiggsps 
production in the gluon fusion ($\Pgluon\Pgluon\phi$) and b-associated ($\Pbottom\Pbottom\phi$) production 
modes (see chapter \ref{chap:theory}) and decay into $\Pgt\Pgt$. 
In addition to the upper limits on \xsbr of these two processes, 
the results are interpreted in \ac{MSSM} benchmark scenarios.
A very similar analysis, not described in detail here,
was performed on a dataset corresponding to $2.3\,\invfb$ collected at $\sqrt{s}=13\,\TeV$ during the 2015 \ac{LHC} p-p running period.  
More information can be found in reference \cite{CMS-PAS-HIG-16-006}.

@@

Signal and background events were generated using
various \ac{MC} event generators. Signal samples
for the $\Pg\Pg \rightarrow \phi$ and $\Pg\Pg \rightarrow \Pbottom\Pbottom\phi$
production processes of the \PHiggs or \PHiggsps bosons were generated using \texttt{PYTHIA 8.1} \cite{pythia81}.
These samples were produced for a range of masses between $90\,\GeV$ and $3.2\,\TeV$.
This range is slightly wider than the range in which MSSM Higgs sector
benchmark computations are available, $90\,\GeV$--$2\,\TeV$, and 
improves on the mass range of $90\,\GeV$ to $1\,\TeV$ that was studied during Run 1 in the context of \ac{BSM} Higgs searches.
\ac{SM} Higgs boson signal samples are used for the interpretation of the analysis results in 
\ac{MSSM} benchmark scenarios. These samples are generated using \texttt{POWHEG} \cite{powheg1,powheg2,powheg3}.

Single-top and \ttbar background samples are generated using \texttt{POWHEG},
with \texttt{MadGraph5\_aMC@NLO} \cite{amcnlo} used for the generation of di-boson background
samples. %and part of the W+$\gamma$ background, which is included in the \emu channel only.
\Wjets and \Zll backgrounds are generated with the \texttt{MadGraph 5} \cite{madgraph}
matrix element generator. Samples containing both a mixture
of jet multiplicities (`inclusive' samples) and samples with one, two, three or four jets (`exclusive' samples)
are generated. These exclusive samples increase the available number of
background events with higher jet multiplicities. %note LO samples used because to get same number of effective
%events would need to generate more NLO samples
The `inclusive' and `exclusive' samples are reweighted
before they are combined so as to preserve the correct
fractions of events with each jet multiplicity. The $\PW{+}\Pphoton$ background samples,
only included in the \emu channel, are generated either with \texttt{MadGraph 5} or 
with \texttt{MadGraph5\_aMC@NLO}.

@@

Other selections include cuts on the transverse and longitudinal impact parameters $d_{xy}$ and $d_{z}$, which
ensure that the particle is likely to have
originated from the primary vertex. This reduces the number of selected particles
which come from pileup interactions.
Additional identification and isolation criteria
are also applied; these will be discussed in sections \ref{sec:mssm_eventsel_pairs}--\ref{sec:mssm_eventsel_em}.
The optimisation of some of the selections will also be discussed there. Note that 
the optimisations were all based on the dataset collected during the 2015 p-p running period of the \ac{LHC}, which
corresponds to an integrated luminosity of $2.3\,\invfb$.

@@

\subsection{\texorpdfstring{Event selection in the \mutau channel}{Event selection in the mu tau channel}}
\label{sec:mssm_eventsel_mt}
The trigger only requires a muon at \ac{L1}, to which loose identification and
isolation criteria are applied at the level of the \ac{HLT}

@@

The choice of the hadronic tau \pT~selection is driven by the effect on the low mass region:
raising the \pT~selection by $10\,\GeV$ from the minimum of $20\,\GeV$ does not affect the sensivity
of the analysis for high mass points, while recovering some of the loss of loosening 
the tau isolation working point and \mT~cut. The reason for this is that when using $\pTm >30\,\GeV$ 
the loss of background events exceeds the loss of signal events. The effect of the increased hadronic tau \pT~selection on the 
upper limits for the $\Pg\Pg\phi$ production process is shown
in figure~\ref{fig:mssm_tauptcut}a, and on the $\Pbottom\Pbottom\phi$ production process
in figure~ \ref{fig:mssm_tauptcut}b. At low mass the improvement in the $\Pg\Pg\phi$ limits
obtained by increasing the \pT~selection is sizeable; for $\Pbottom\Pbottom\phi$ events the effect is much
less pronounced.

@@

\subsection{\texorpdfstring{Event selection in the \tautau channel}{Event selection in the tau tau channel}}
\label{sec:mssm_eventsel_tt}
The trigger in the \tautau channel requires two hadronic taus at \ac{L1} to which loose identification
and isolation criteria are applied in the \ac{HLT}

@@

Figure \ref{fig:mssm_cats_mt}a shows the number of jets 
in the \mutau channel, with figure \ref{fig:mssm_cats_mt}b showing
the number of b-tagged jets in that channel. The gluon fusion
and b-associated signals are overlaid on these distributions, normalised
to 100 times their \xsbr at \mA~$=1\,\TeV$ and 
\tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$ scenario. 
The distribution of the
gluon fusion signal in figure \ref{fig:mssm_cats_mt}b shows that
the vast majority of these signal events do not have any b-tagged jets. To
target this production mode a category which requires nob-tagged jets can be used.
The same figure also shows that the majority of $\Pbottom\Pbottom\phi$
signal events do not have any b-tagged jets: either the b-jets in these events 
are too soft, or they do not pass the b-tagging requirements. This means that the category
which requires no b-tagged jets
is also sensitive to some of the $\Pbottom\Pbottom\phi$ signal. To target the remainder of 
the $\Pbottom\Pbottom\phi$ signal, another category with at least one b-tagged jet is defined. 
The $\Pbottom\Pbottom\phi$ signal in figure \ref{fig:mssm_cats_mt}b shows that there is not
such a large proportion of events with more than one b-tagged jet. Figure \ref{fig:mssm_cats_mt}a
shows that the \ttbar background starts to become larger for events with more than
one jet. The definition of the category that targets the $\Pbottom\Pbottom\phi$ signal is therefore chosen with the inclusion
of a jet veto, such that the region where the \ttbar background becomes larger is excluded, 
while retaining a large proportion of the $\Pbottom\Pbottom\phi$ signal.

In summary, the two categories are defined as:
\begin{itemize}
\setlength{\itemsep}{-\baselineskip}
\item \textbf{No b-tag}: No b-tagged jets. This category targets the $\Pg\Pg\phi$ production mode but is also sensitive to some of the $\Pbottom\Pbottom\phi$ signal.
\item \textbf{B-tag}: At least one b-tagged jet, at most one 
jet with $\pTm>30\,\GeV$. This second requirement, the jet veto, reduces the \ttbar background. 
Due to the lower \pT~requirement considered for
b-tagging compared with the requirement for the jet veto, it is still possible for there
to be more than one b-tagged jet in the event.
\end{itemize}

@@

\section{Background estimation}
\label{sec:mssm_bkgs}
There are several backgrounds in this analysis, and the different final
states can have different background compositions. Consider figure \ref{fig:mssm_bkgs_overview}a,
which shows the low $m_{\text{T}}^{\text{tot}}$ region in the no b-tag category
of the \mutau channel and figure \ref{fig:mssm_bkgs_overview}b, which shows the low $m_{\text{T}}^{\text{tot}}$
region in the b-tag category of the \emu channel. These regions are where the backgrounds are concentrated and it
is therefore easier to see the different contributions. \Ztautau is a background in all four channels as 
it has two real taus in the final state, like the signal being searched for. 
Smaller backgrounds 
from \Zellell decays also play a role, especially in the \mutau and \etau channels where such events
might pass the selection if, for example, one of the leptons or a jet is mis-reconstructed as a hadronic tau.
Production of QCD multijet events, labelled `QCD' in figure \ref{fig:mssm_bkgs_overview}, is a background when 
two jets are mis-reconstructed as the two tau candidates. %Relatively likely to happen in tautau channel
As is visible in figure \ref{fig:mssm_bkgs_overview}b, the \ttbar background is particularly important in the b-tag category.
This is because top quarks virtually always decay as $\Ptop\rightarrow \PW\Pbottom$, and so such events nearly 
always contain b-jets. The decay products of one or both of the \PW bosons, and additional jets in the event, can 
then form \etau, \mutau, \tautau and \emu pairs.\\
The \Wjets process is a background in the \etau and \mutau channels when the lepton from the \PW boson decay and a jet mis-reconstructed
as a hadronic tau form a pair. In the \tautau channel it is a background when one \Pgth originates from a $\PW \rightarrow \Pgt\Pgn$ decay
and the other from an additional jet in the event being mis-reconstruced as a hadronic tau. 
In the \emu channel an additional lepton would have to originate from one of the jets, and so in this
channel this background is smaller. The di-boson and single-top backgrounds are small in all channels. In
figures the di-boson and single-top backgrounds are drawn together with the \Wjets 
background and labelled collectively as the `Electroweak' component.

@@

\subsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
\label{sec:mssm_bkgs_ztt}
For all channels, both the shape and normalisation of the \Ztautau background 
are estimated from the Drell-Yan
simulation.
For the \mutau and \etau channels, events
in which the reconstructed hadronic tau is matched to 
a simulated hadronic tau are considered part of the \Ztautau
background. In the \tautau channel both reconstructed
hadronic taus are required to be matched to a simulated hadronic tau, and
in the \emu channel the \Ztautau component of the Drell-Yan background 
is taken as those events where the reconstructed electron is not matched to
a simulated prompt electron and the reconstructed
muon is not matched to a prompt muon. 
Events in the Drell-Yan simulation 
that do not satisfy the generator matching requirements are considered
as the much smaller \Zellell background.
%To correct and constrain the \Ztautau normalisation in the
%b-tag and no b-tag categories of all channels, \Zmm control
%regions are considered in a simultaneous fit with the signal region. More detail is given in 
%section \ref{sec:mssm_sigext_ctrl}.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_002.pdf}
\end{center}
\caption[Distribution of the transverse mass \mT~in the \mutau channel, indicating the signal region and the high-\mT~control region]{Distribution of the transverse mass \mT~in the \mutau channel, indicating
the signal region and the high-\mT~control region. This distribution is shown
before dividing the events into categories \cite{CMS-PAS-HIG-16-037}.}
\label{fig:mssm_bkgs_wjets_mutau_mt}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[Pre-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_far_et_1_prefit.png}}
\subfloat[Post-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_far_et_1_postfit.png}}
\end{center}
\caption[The visible mass distribution of the di-tau pair
in the \etau channel for the sideband further away from the signal
region, before and after the maximum likelihood fit to $R_{\text{QCD}}^{\text{OS/SS}}$.]{The visible 
mass distribution of the di-tau pair in the \etau channel for the sideband further away from the signal region, (a) before
the maximum likelihood fit to $R_{\text{QCD}}^{\text{OS/SS}}$ and (b) after the fit. The resulting value of $R_{\text{QCD}}^{\text{OS/SS}}$
is $1.13\pm0.05$.}
\label{fig:mssm_qcdosss_etfar}
\end{figure}

@@

@@

by shifting the jet energy up and down by a \pT-and $\eta$-dependendent

@@

\setlength{\itemsep}{-\baselineskip}

@@

Overview tables of the systematic uncertainties per category of each
channel can be found in appendix \ref{appendix:uncerts}. The correlations
between the different channels and categories for these uncertainties
is also indicated.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_em_8_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_em_9_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
\end{center}
\caption[Transverse component of the di-tau mass for the expected backgrounds
and observed events in the no b-tag and b-tag categories of the \emu channel.]{Transverse component of the di-tau mass for the expected backgrounds and
observed events in the (a) no b-tag and (b) b-tag categories of the \emu channel.}
%The signal overlaid corresponds to the signal of the three Higgs bosons at \mA=1 TeV and \tanb=50
%in the $m_{\text{h}}^{\text{mod+}}$ scenario, and so it peaks once at low mass, for the light Higgs boson,
%and once at higher mass, for the heavy H and A.}
\label{fig:mssm_hig16006_mtsv_em}
\end{figure}

@@

The correlation scheme is chosen
based on the procedure used for the ATLAS and \ac{CMS}
Higgs combinations \cite{MassComb,CouplComb}. This means
uncertainties are either considered 100\% (anti-)correlated or fully uncorrelated. Partial
correlations are not taken into account, with a small number of exceptions. The
correlations used for this combination are given in table \ref{tab:mssm_combination_correlations},
with the motivation for the chosen correlation given in the third column of the table.
The chosen correlation scheme is motivated
by carefully considering the differences between the two analyses
and the conditions under which they were performed.

>>>>

\chapter{\texorpdfstring{Search for MSSM \AHtotautau}{Search for MSSM A/H -->tautau}}
\label{chap:mssm}
In this chapter the search for neutral Higgs bosons \PHiggs or \PHiggsps
decaying to a pair of tau leptons is discussed. The results presented
here correspond to those from an analysis performed on a dataset collected
during the first half of the 2016 p-p running period of the \ac{LHC} \cite{CMS-PAS-HIG-16-037}. %This dataset
%corresponds to an integrated luminosity of $12.9\,\invfb$, and the analysis is
%detailed in reference \cite{CMS-PAS-HIG-16-037}. 
The \etau, \mutau, \tautau and \emu final
states of the di-tau pair were studied. The results of this search are 
model-independent upper limits on \xsbr of \PHiggs or \PHiggsps 
production in the gluon fusion ($\Pgluon\Pgluon\phi$) and b-associated ($\Pbottom\Pbottom\phi$) production 
modes (see chapter \ref{chap:theory}) and decay into $\Pgt\Pgt$. 
In addition to the upper limits on \xsbr of these two processes, 
the results are interpreted in \ac{MSSM} benchmark scenarios.
A very similar analysis, not described in detail here,
was performed on a dataset corresponding to $2.3\,\invfb$ collected at $\sqrt{s}=13\,\TeV$ during the 2015 \ac{LHC} p-p running period.  
More information can be found in reference \cite{CMS-PAS-HIG-16-006}.

@@

Signal and background events are generated using
various \ac{MC} event generators. Signal samples
for the $\Pg\Pg \rightarrow \phi$ and $\Pg\Pg \rightarrow \Pbottom\Pbottom\phi$
production processes of the \PHiggs or \PHiggsps bosons are generated using \texttt{PYTHIA 8.1} \cite{pythia81}.
These samples are produced for a range of masses between $90\,\GeV$ and $3.2\,\TeV$.
This range is slightly wider than the range in which MSSM Higgs sector
benchmark computations are available, $90\,\GeV$--$2\,\TeV$, and 
improves on the mass range of $90\,\GeV$ to $1\,\TeV$ that was studied during Run 1 in the context of \ac{BSM} Higgs searches.
\ac{SM} Higgs boson signal samples are used for the interpretation of the analysis results in 
\ac{MSSM} benchmark scenarios. These samples are generated using \texttt{POWHEG} \cite{powheg1,powheg2,powheg3}.

Single-top and \ttbar background samples are generated using \texttt{POWHEG},
while for the generation of di-boson background samples \texttt{MadGraph5\_aMC@NLO} \cite{amcnlo} is used.
%and part of the W+$\gamma$ background, which is included in the \emu channel only.
\Wjets and \mbox{\Zll} backgrounds are generated with the \texttt{MadGraph 5} \cite{madgraph}
matrix element generator. Samples containing both a mixture
of jet multiplicities (`inclusive' samples) and samples with one, two, three or four jets (`exclusive' samples)
are generated. These exclusive samples increase the available number of
background events with higher jet multiplicities. %note LO samples used because to get same number of effective
%events would need to generate more NLO samples
The `inclusive' and `exclusive' samples are reweighted
before they are combined so as to preserve the correct
fractions of events with each jet multiplicity. The $\PW{+}\Pphoton$ background samples,
only included in the \emu channel, are generated either with \texttt{MadGraph 5} or 
with \texttt{MadGraph5\_aMC@NLO}.

@@

Other selections include cuts on the transverse and longitudinal impact parameters $d_{xy}$ and $d_{z}$, which
ensure that the particle is likely to have
originated from the primary vertex. This reduces the number of selected particles
which come from pileup interactions.
Additional identification and isolation criteria
are also applied; these will be discussed in sections \ref{sec:mssm_eventsel_pairs}--\ref{sec:mssm_eventsel_em}.
The optimisation of some of the selections will also be discussed there. Note that 
the optimisations are all based on the dataset collected during the 2015 p-p running period of the \ac{LHC}, which
corresponds to an integrated luminosity of $2.3\,\invfb$.

@@

\subsection{\texorpdfstring{Event selection in the \mutau channel}{Event selection in the mu tau channel}}
\label{sec:mssm_eventsel_mt}
The trigger only requires a muon at \ac{L1}, to which loose identification and
isolation criteria are applied at the level of the \ac{HLT}.

@@

The choice of the hadronic tau \pT~selection is driven by the effect on the low mass region:
raising the \pT~selection by $10\,\GeV$ from the minimum of $20\,\GeV$ does not affect the sensitivity
of the analysis for high mass points, while recovering some of the loss of loosening 
the tau isolation working point and \mT~cut. The reason for this is that when using $\pTm >30\,\GeV$ 
the loss of background events exceeds the loss of signal events. The effect of the increased hadronic tau \pT~selection on the 
upper limits for the $\Pg\Pg\phi$ production process is shown
in figure~\ref{fig:mssm_tauptcut}a, and on the $\Pbottom\Pbottom\phi$ production process
in figure~ \ref{fig:mssm_tauptcut}b. At low mass the improvement in the $\Pg\Pg\phi$ limits
obtained by increasing the \pT~selection is sizeable; for $\Pbottom\Pbottom\phi$ events the effect is much
less pronounced.

@@

\subsection{\texorpdfstring{Event selection in the \tautau channel}{Event selection in the tau tau channel}}
\label{sec:mssm_eventsel_tt}
The trigger in the \tautau channel requires two hadronic taus at \ac{L1} to which loose identification
and isolation criteria are applied in the \ac{HLT}.

@@

Figure \ref{fig:mssm_cats_mt}a shows the number of jets 
in the \mutau channel, with figure \ref{fig:mssm_cats_mt}b showing
the number of b-tagged jets in that channel. The gluon fusion
and b-associated signals are overlaid on these distributions, normalised
to 100 times their \xsbr at \mA~$=1\,\TeV$ and 
\tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$ scenario. 
The distribution of the
gluon fusion signal in figure \ref{fig:mssm_cats_mt}b shows that
the vast majority of these signal events do not have any b-tagged jets. To
target this production mode a category which requires no b-tagged jets can be used.
The same figure also shows that the majority of $\Pbottom\Pbottom\phi$
signal events do not have any b-tagged jets: either the b-jets in these events 
are too soft, or they do not pass the b-tagging requirements. This means that the category
which requires no b-tagged jets
is also sensitive to some of the $\Pbottom\Pbottom\phi$ signal. To target the remainder of 
the $\Pbottom\Pbottom\phi$ signal, another category with at least one b-tagged jet is defined. 
The $\Pbottom\Pbottom\phi$ signal in figure \ref{fig:mssm_cats_mt}b shows that there is not
such a large proportion of events with more than one b-tagged jet. Figure \ref{fig:mssm_cats_mt}a
shows that the \ttbar background starts to become larger for events with more than
one jet. The definition of the category that targets the $\Pbottom\Pbottom\phi$ signal is therefore chosen with the inclusion
of a jet veto, such that the region where the \ttbar background becomes larger is excluded, 
while retaining a large proportion of the $\Pbottom\Pbottom\phi$ signal.

In summary, the two categories are defined as:
\begin{itemize}
\setlength{\itemsep}{-0.5\baselineskip}
\item \textbf{No b-tag}: No b-tagged jets. This category targets the $\Pg\Pg\phi$ production mode but is also sensitive to some of the $\Pbottom\Pbottom\phi$ signal.
\item \textbf{B-tag}: At least one b-tagged jet, at most one 
jet with $\pTm>30\,\GeV$. This second requirement, the jet veto, reduces the \ttbar background. 
Due to the lower \pT~requirement considered for
b-tagging compared with the requirement for the jet veto, it is still possible for there
to be more than one b-tagged jet in the event.
\end{itemize}

@@

\section{Background estimation}
\label{sec:mssm_bkgs}
There are several backgrounds in this analysis, and the different final
states can have different background compositions. Consider figure \ref{fig:mssm_bkgs_overview}a,
which shows the low $m_{\text{T}}^{\text{tot}}$ region in the no b-tag category
of the \mutau channel and figure \ref{fig:mssm_bkgs_overview}b, which shows the low $m_{\text{T}}^{\text{tot}}$
region in the b-tag category of the \emu channel. These regions are where the backgrounds are concentrated and it
is therefore easier to see the different contributions. \Ztautau is a background in all four channels as 
it has two real taus in the final state, like the signal being searched for. 
Smaller backgrounds 
from \Zellell decays also play a role, especially in the \mutau and \etau channels where such events
might pass the selection if, for example, one of the leptons or a jet is mis-reconstructed as a hadronic tau.
Production of QCD multijet events, labelled `QCD' in figure \ref{fig:mssm_bkgs_overview}, is a background when 
two jets are mis-reconstructed as the two tau candidates. %Relatively likely to happen in tautau channel
As is visible in figure \ref{fig:mssm_bkgs_overview}b, the \ttbar background is particularly important in the b-tag category.
This is because top quarks virtually always decay as $\Ptop\rightarrow \PW\Pbottom$, and so such events nearly 
always contain b-jets. The decay products of one or both of the \PW bosons, and additional jets in the event, can 
then form \etau, \mutau, \tautau and \emu pairs.

The \Wjets process is a background in the \etau and \mutau channels when the lepton from the \PW boson decay and a jet mis-reconstructed
as a hadronic tau form a pair. In the \tautau channel it is a background when one \Pgth originates from a $\PW \rightarrow \Pgt\Pgn$ decay
and the other from an additional jet in the event being mis-reconstruced as a hadronic tau. 
In the \emu channel an additional lepton would have to originate from one of the jets, and so in this
channel this background is smaller. The di-boson and single-top backgrounds are small in all channels. In
figures the di-boson and single-top backgrounds are drawn together with the \Wjets 
background and labelled collectively as the `Electroweak' component.

@@

\subsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
\label{sec:mssm_bkgs_ztt}
For all channels, both the shape and normalisation of the \Ztautau background 
are estimated from the Drell-Yan
simulation.
For the \mutau and \etau channels, events
in which the reconstructed hadronic tau is matched to 
a simulated hadronic tau are considered part of the \Ztautau
background. In the \tautau channel both reconstructed
hadronic taus are required to be matched to a simulated hadronic tau. 
In the \emu channel the \Ztautau component of the Drell-Yan background 
is taken as those events where the reconstructed electron is not matched to
a simulated prompt electron and the reconstructed
muon is not matched to a prompt muon. 
Events in the Drell-Yan simulation 
that do not satisfy the generator matching requirements are considered
as the much smaller \Zellell background.
%To correct and constrain the \Ztautau normalisation in the
%b-tag and no b-tag categories of all channels, \Zmm control
%regions are considered in a simultaneous fit with the signal region. More detail is given in 
%section \ref{sec:mssm_sigext_ctrl}.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_002.pdf}
\end{center}
\caption[Distribution of the transverse mass \mT~in the \mutau channel, indicating the signal region and the high-\mT~control region.]{Distribution of the transverse mass \mT~in the \mutau channel, indicating
the signal region and the high-\mT~control region. This distribution is shown
before dividing the events into categories \cite{CMS-PAS-HIG-16-037}.}
\label{fig:mssm_bkgs_wjets_mutau_mt}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[Pre-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_far_et_1_prefit.png}}
\subfloat[Post-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_far_et_1_postfit.png}}
\end{center}
\caption[The visible mass distribution of the di-tau pair
in the \etau channel for the sideband further away from the signal
region, before and after the maximum likelihood fit to $R_{\text{QCD}}^{\text{OS/SS}}$.]{The visible 
mass distribution of the di-tau pair in the \etau channel for the sideband further away from the signal region, (a) before
the maximum likelihood fit to $R_{\text{QCD}}^{\text{OS/SS}}$ and (b) after the fit. The resulting value of $R_{\text{QCD}}^{\text{OS/SS}}$
is $1.13\pm0.05$.}
\label{fig:mssm_qcdosss_etfar}
\end{figure}
\clearpage

@@

Overview tables of the systematic uncertainties per category of each
channel can be found in appendix \ref{appendix:uncerts}. The correlations
between the different channels and categories for these uncertainties
are also indicated.

@@

by shifting the jet energy up and down by a \pT- and $\eta$-dependent

@@

\setlength{\itemsep}{-0.5\baselineskip}

@@

@@

\begin{figure}[h!]
\begin{center}
\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_em_8_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_em_9_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
\end{center}
\caption[Transverse component of the di-tau mass for the expected backgrounds
and observed events in the no b-tag and b-tag categories of the \emu channel.]{Transverse component of the di-tau mass for the expected backgrounds and
observed events in the (a) no b-tag and (b) b-tag categories of the \emu channel.}
%The signal overlaid corresponds to the signal of the three Higgs bosons at \mA=1 TeV and \tanb=50
%in the $m_{\text{h}}^{\text{mod+}}$ scenario, and so it peaks once at low mass, for the light Higgs boson,
%and once at higher mass, for the heavy H and A.}
\label{fig:mssm_hig16006_mtsv_em}
\end{figure}
\clearpage

@@

The correlation scheme is chosen
based on the procedure used for the ATLAS and \ac{CMS}
Higgs combinations \cite{MassComb,CouplComb}. This means
uncertainties are either considered 100\% \mbox{(anti-)correlated} or fully uncorrelated. Partial
correlations are not taken into account, with a small number of exceptions. The
correlations used for this combination are given in table \ref{tab:mssm_combination_correlations},
with the motivation for the chosen correlation given in the third column of the table.
The chosen correlation scheme is motivated
by carefully considering the differences between the two analyses
and the conditions under which they were performed.

### 2017-03-08 MSSM/UncOv.tex
Final bits before submission

\caption[Systematic uncertainties that affect the estimated number of signal or background events in the \mutau channel]{\footnotesize Systematic uncertainties that affect the estimated number of signal

>>>>

\caption[Systematic uncertainties that affect the estimated number of signal or background events in the \mutau channel.]{\footnotesize Systematic uncertainties that affect the estimated number of signal
